### 2014-03-12 src/methodology.Rnw
update

We ran mutation analysis on this set of projects using
PIT\cite{pitest}. However, since the operators provided by PIT are limited,
we extended PIT to provide newer operators that are similar to operators
provided by other mutation systems. The set of operators that we used
are provided in Table~\ref{tbl:pitop}. A distribution of these operators
in our projects are provided in Figure~\ref{fig:op}, which shows both the
distribution of complete mutants and the relative detection rates of each
mutation operators. For a detailed description of each, please see~\cite{pitmut}

Further, we also modified PIT to provide random selection of mutants according
to various criterias.

@@

Finally, to remove random noice, each criteria described has been run four times, and the results are averaged to produce the final result.

>>>>

We ran mutation analysis on this set of projects using
PIT\cite{pitest}. However, since the operators provided by PIT are limited,
we extended PIT to provide newer operators that are similar to operators
provided by other mutation systems. The set of operators that we used
are provided in Table~\ref{tbl:pitop}. A distribution of these operators
in our projects are provided in Figure~\ref{fig:op}, which shows both the
distribution of complete mutants and the relative detection rates of each
mutation operators. In the figure, there are two box-plots corresponding
to each mutation operator on the Y-axis. The black box represents the
relative frequency of the particular mutation operator in the total mutants
\textit{generated}. For example for projects in the randoop set, the
operator \pitnvmc contributed about 23\% of the total number of mutants
produced while \pitrv contributed about 15\%. Similarly, the blue shaded
box-plot represents the relative frequency of particular mutation operator
in the total mutants \textit{detected}. For example, \pitnvmc contribution
in the detected mutants was 34\% while that of \pitrv was 7\%.

For a detailed description of each mutants, please see~\cite{pitmut}.
PIT was also modifed to provide random selection of mutants according
to various criterias. Finally, to remove random noice, each criteria
described has been run four times, and the results are averaged to produce
the final result.

@@
